---
title: "epivizr"
output: html_document
---

```{r setup, include=FALSE}
opts_chunk$set(eval=FALSE)
```

**Purpose**: Interactive visualization of genomic data in a browser. Supports Bioconductor data structures such as `GenomicRanges` and `SummarizedExperiments`. 

**Citations**: 

* [Chelaru et al. (2014)](http://www.nature.com/nmeth/journal/v11/n9/full/nmeth.3038.html) 

To install the `epivizr` R/Bioconductor package
```{r}
source("http://bioconductor.org/biocLite.R")
biocLite("epivizr")
library(epivizr)
```

# `epivizr` Workflow

```{r}
mgr <- startEpiviz() # Opens epiviz in the browser and starts a new session

# Line plot of methylation data at base-pair resolution 
mgr$addDevice(GRangesObject, "450kMeth", type="bp", columns = IDs)

# Scatter plot comparing the M-values and A-values in an MA plot
mat # data frame with "Avals" and "Mvals" as column names
assayDataElement(GRangesObject, "MA") <- mat
show(GRangesObject)
mgr$addDevice(GRangesObject, "MAPlot", columns = c("Avals", "Mvals"), assay = "MA")


mgr$stopServer() # closing the epiviz session
```

#### Starting a new epiviz session

* `startEpiviz()` = opens epiviz in the browser and starts a new interactive session between R and the browser

#### Examples

* `mgr$addDevice(GRangesObject, "450kMeth", type="bp", columns = ...)` = Line plot of methylation data at base-pair resolution 
* `mgr$addDevice(GRangesObject, "MAPlot", columns = ..., assay = ...)` = Scatter plot (MA plot) using an `MA` data frame that was added using `assayDataElement(GRangesObject, "MA") <- mat` where `mat` has columns `Avals` and `Mvals`. 
* 

#### Other

* `mgr$rmAllDevices()` = removes all plots added in current session
* `mgr$listDevice()` = list all devices added in current session
* `mgr$navigate(chr = ..., start = ... , end = ...)` = Move to a specific region in the genome defined by `chr`, `start` and `end`
* `mgr$slideshow(regionsObject, n = ...)` = create a slide show of the top n regions 
     

#### Closing an epiviz session

* `mgr$stopServer()` = closes the epiviz interactive session betwee R and the browser

